Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-03-25 paper/zhang-cook-laa-langrene-menendez.Rmd
changes according to ursula's ntoes

The goal of continuous optimisation is to find the best solution within the space of all feasible solutions where typically the best solution is defined via an objective function. Broadly speaking, optimization can be unconstrained or constrained [@kelley1999iterative]. The unconstrained problem can be formulated as a minimization (or maximization)  problem such as 
$\min_{x} f(x)$ where $f:\mathbb{R}^n \rightarrow \mathbb{R}$ is an objective function with certain properties defined in an $L^p$ space. In this case, solutions rely on gradient descent or ascent methods. In the constrained optimization problem additional restrictions  are introduced via a set of functions that can be convex or non-convex: $g_i:\mathbb{R}^n \rightarrow \mathbb{R}$ for $i = 1, \ldots k$ and hence the problem can be written as
$\min_{x} f(x)$ *subject to* $g_i(x) \leq 0$. Here methods such as multipliers and convex optimization methods including linear and quadratic programming can be used.

@@

```{r toy-search, fig.cap="A comparison of the searches by two optimisers: CRS (left) and SA (right) on a 2D projection problem of a six-variable dataset, \\code{boa6} using holes index. Both optimisers reach the final basis with a similar index value while it takes SA longer to find the final basis."}
```

@@

Random variables with different distributions have been simulated and the distributional form of each variable is presented in equations \ref{eq:sim-norm} to \ref{eq:sim-x7}. Variables `x1`, `x8`, `x9` and `x10` are normal noise with zero mean and unit variance and `x2` to `x7` are normal mixtures with varied weights and locations. All the variables have been scaled to have an overall unit variance before projection pursuit.

>>>>

<!-- The goal of continuous optimisation is to find the best solution within the space of all feasible solutions where typically the best solution is defined via an objective function. Broadly speaking, optimization can be unconstrained or constrained [@kelley1999iterative]. The unconstrained problem can be formulated as a minimization (or maximization)  problem such as  -->
<!-- $\min_{x} f(x)$ where $f:\mathbb{R}^n \rightarrow \mathbb{R}$ is an objective function with certain properties defined in an $L^p$ space. In this case, solutions rely on gradient descent or ascent methods. In the constrained optimization problem additional restrictions  are introduced via a set of functions that can be convex or non-convex: $g_i:\mathbb{R}^n \rightarrow \mathbb{R}$ for $i = 1, \ldots k$ and hence the problem can be written as -->
<!-- $\min_{x} f(x)$ *subject to* $g_i(x) \leq 0$. Here methods such as multipliers and convex optimization methods including linear and quadratic programming can be used. -->

@@

```{r toy-search, fig.cap="A comparison of the searches by two optimisers: CRS (left) and SA (right) on a 2D projection problem of a six-variable dataset, \\code{boa6} using holes index. Both optimisers reach the final basis with a similar index value while it takes SA longer to find the final basis. In the earlier iterations, optimisers quickly find a better basis to proceed while in the later iterations, most sampled bases fail to make an improvement on the index value and boxplot is used to summarise the distribution of the index values. There is no better basis found in the last iteration, 9 (left) and 15 (right), before reaching the maximum number of try and hence it is colored grey."}
```

@@

Random variables with different distributions have been simulated and the distributional form of each variable is presented in equations \ref{eq:sim-norm} to \ref{eq:sim-x7}. Variables `x1`, `x8`, `x9` and `x10` are normal noise with zero mean and unit variance and `x2` to `x7` are normal mixtures with varied weights and locations. All the variables have been scaled to have an overall unit variance before projection pursuit. Holes index [@cook2008grand], used for detecting binormality of the variables, is used throughout the examples unless otherwise specified.

### 2021-03-25 paper/zhang-cook-laa-langrene-menendez.tex
changes according to ursula's ntoes

The goal of continuous optimisation is to find the best solution within
the space of all feasible solutions where typically the best solution is
defined via an objective function. Broadly speaking, optimization can be
unconstrained or constrained \citep{kelley1999iterative}. The
unconstrained problem can be formulated as a minimization (or
maximization) problem such as \(\min_{x} f(x)\) where
\(f:\mathbb{R}^n \rightarrow \mathbb{R}\) is an objective function with
certain properties defined in an \(L^p\) space. In this case, solutions
rely on gradient descent or ascent methods. In the constrained
optimization problem additional restrictions are introduced via a set of
functions that can be convex or non-convex:
\(g_i:\mathbb{R}^n \rightarrow \mathbb{R}\) for \(i = 1, \ldots k\) and
hence the problem can be written as \(\min_{x} f(x)\) \emph{subject to}
\(g_i(x) \leq 0\). Here methods such as multipliers and convex
optimization methods including linear and quadratic programming can be
used.

@@

\caption[A comparison of the searches by two optimisers]{A comparison of the searches by two optimisers: CRS (left) and SA (right) on a 2D projection problem of a six-variable dataset, \code{boa6} using holes index. Both optimisers reach the final basis with a similar index value while it takes SA longer to find the final basis.}\label{fig:toy-search}
\end{figure}
\end{Schunk}

@@

Random variables with different distributions have been simulated and
the distributional form of each variable is presented in equations
\ref{eq:sim-norm} to \ref{eq:sim-x7}. Variables \texttt{x1},
\texttt{x8}, \texttt{x9} and \texttt{x10} are normal noise with zero
mean and unit variance and \texttt{x2} to \texttt{x7} are normal
mixtures with varied weights and locations. All the variables have been
scaled to have an overall unit variance before projection pursuit.

>>>>

@@

\caption[A comparison of the searches by two optimisers]{A comparison of the searches by two optimisers: CRS (left) and SA (right) on a 2D projection problem of a six-variable dataset, \code{boa6} using holes index. Both optimisers reach the final basis with a similar index value while it takes SA longer to find the final basis. In the earlier iterations, optimisers quickly find a better basis to proceed while in the later iterations, most sampled bases fail to make an improvement on the index value and boxplot is used to summarise the distribution of the index values. There is no better basis found in the last iteration, 9 (left) and 15 (right), before reaching the maximum number of try and hence it is colored grey.}\label{fig:toy-search}
\end{figure}
\end{Schunk}

@@

Random variables with different distributions have been simulated and
the distributional form of each variable is presented in equations
\ref{eq:sim-norm} to \ref{eq:sim-x7}. Variables \texttt{x1},
\texttt{x8}, \texttt{x9} and \texttt{x10} are normal noise with zero
mean and unit variance and \texttt{x2} to \texttt{x7} are normal
mixtures with varied weights and locations. All the variables have been
scaled to have an overall unit variance before projection pursuit. Holes
index \citep{cook2008grand}, used for detecting binormality of the
variables, is used throughout the examples unless otherwise specified.
